Report on Late Winter2013 Production: Image Differencing

### 2013-03-25 W13report.tex
Last checking before leaving for weekend.  ACB
Detail that visit 2 yields a deconvolution for 5/9 sensors

@@

A template image was generated by {\bf DETAIL}.  The template has a
seeing of 0.88''.  This means that the matching of the template image
with visit 6866601 will yield a template {\it deconvolution} in the
postfilter configuration.  The matching of the template with 6866601
in the prefilter configuration, and with 6866602 in the postfilter
configuration, will yield a small convolution, since both images will
have a FWHM of 0.8--0.9''.  All other Psf--matching operations will
yield a significant convolution of the template image.

@@

To quantify the significance of these offsets, we compared the
empirical variance in the image planes with the variance tracked by
the variance planes to ascertain how much we are misestimating the
true variance.  We calculated the ratio of the interquartile range of
unmasked pixels in the image plane, multiplied by 0.741 and then
squared, with the median of unmasked pixels from the variance plane.
The results are summarized in Table~\ref{tab-variance1}.  We find that
we are marginally, but consistently, underestimating the variance in
our images by $\sim 1\%$.  This affect is smaller than the amplitudes
reported above, indicating that there are true differences in the
variances of prefiltered and postfiltered detection images.

>>>>

Compare the measured S/N of the DiaSources with the detection threshold.

@@

A template image was generated by {\bf DETAIL}.  The template has a
seeing of 0.88''.  This means that the matching of the template image
with visit 6866601 will yield a template {\it deconvolution} in the
postfilter configuration.  Matching of the template image with visit
6866602 also yields a mild deconvolution (the images were generated to
have the same seeing) for 5/9 sensors.  The matching of the template
with visit 6866603 with postfiltering, and of all visits with
prefiltereing, yields a convolution (smoothing) of the image.

@@

To quantify the significance of these offsets, we compared the
empirical variance in the image planes with the variance tracked by
the variance planes to ascertain how much we are misestimating the
true variance.  We calculated the ratio of the interquartile range of
unmasked pixels in the image plane, multiplied by 0.741 and then
squared, with the median of unmasked pixels from the variance plane.
The results are summarized in Table~\ref{tab-variance1}.  We find that
we are marginally, but consistently, underestimating the variance in
our images by $\sim 1\%$.  This affect is smaller than the amplitudes
reported above, indicating that there are true differences in the
variances of prefiltered and postfiltered detection images.  As the
variance is higher in the prefiltered images, we will be slightly less
sensitive to true variability.
